Capturing Policies for BYOD

### 2016-10-13 paper.tex
updates

\usepackage{listings}

@@

\subsection{BYOD Policies}
Policies were taken from 5 sources:
\begin{itemize}
  \item SANS
  \item NHS
  \item HiMMS
  \item Edinburgh
  \item Code3SPE
\end{itemize}
\todo{Describe differences and similaritites at a high level between these policies.}

>>>>

\usepackage{listings}
\lstdefinelanguage{AppPAL}{%
  morekeywords={if,inf,says,where,true,false,with,is},
  otherkeywords={can-act-as,can-say},
  sensitive=true,
  morestring=[b]',
  literate={\ inf\ }{{$\infty$}}5
}[keywords,strings]
\lstset{%
  basicstyle=\ttfamily,
  keywordstyle=\ttfamily\slshape,
  stringstyle=\sffamily,
  columns=flexible,
  mathescape,
  tabsize=2,
  showstringspaces=true,
  %numbers=left,
  breaklines=true,
  numberstyle=\tiny\ttfamily\color{Gray},
  commentstyle=\ttfamily\color{Gray}
}
\newcommand{\code}[2][]{\lstinline[breaklines=true, #1]{#2}}

@@

\subsection{BYOD Policies}

We analysed five different policies to find common idioms.
The first is the \emph{Security Policy Template: Use of Handheld Devices in a Corporate Environment}, published by the SANS Institute~\cite{nicholas_r._c._guerin_security_2008}.
This is a hypothetical policy published to help companies mitigate the threats to corporate assets caused by mobile devices. 
Companies are expected to modify the document to suit their needs.  The policy is general; not specific to any particular industry, device, or country's legislation.

The second is taken from HiMMS.

\begin{itemize}
  \item SANS
  \item NHS
  \item HiMMS
  \item Edinburgh
  \item Code3SPE
\end{itemize}
\todo{Describe differences and similaritites at a high level between these policies.}
